Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Created a table with an example of generated abstract

\usepackage[english]{babel}
\usepackage{url}

@@

% \section{Research design and methods}

% We will be applying existing discrete GANs to the data collected from arXiv. One of the lates successful models  for scientific text summarization will be selected as our baseline.

@@

Let $s$ be the generated summary. If $|s|$ is the number of words in summary $s$, then $m=|s|-n+1$ is the number of $n$-grams in this summary. Let $s_1, s_2, \dots, s_m$ be all $n$-grams of summary $s$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important $n$-grams in the document. As we will show in section \ref{sec:importance}, there are many ways of measuring the importance of $n$-grams in a document.

@@

\[ \text{CAROUGE-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]

@@

\subsection{TextRank}
\subsection{Seq2Seq}
We have used seq2seq model with attention for a task of text summarization. Seq2seq have proven to provide state-of-art result in tasks of sequence generation.
As input model takes paper abstract converted to the vectorized representation using word embeddings.  The input sequence is limited by 600 words. All abstracts that are bigger than limit are omitted. All smaller abstracts are padded with $\langle\text{SOS}\rangle$ word that represents the end of a sequence.
Model outputs sequence derived from the probability distribution. Each output word samples from this distribution having input sequence and previously generated samples. Output sequence is limited by 30 words. First $\langle\text{SOS}\rangle$ word represent the end of a generated summary.

@@

\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} \\
\hline
TextRank & 0 & 0 & 0 \\
LSTM & 0 & 0 & 0 \\
SeqGAN & 0 & 0 & 0 \\
\hline
\end{tabular}

@@

% \subsection{Timeframes}

% \paragraph{Deliverables for the $1^{st}$ evaluation}
% \begin{itemize}
% \item Dataset of papers collected from arXiv
% \item Results of feature extraction
% \item Implementations of the baseline state-of-the-art model and its application to our dataset
% \end{itemize}

% \paragraph{Deliverables for the $2^{nd}$ (final) evaluation}
% \begin{itemize}
% \item Implementation of several discrete GAN models
% \item Evaluation of the created models on our dataset
% \item Paper describing the results of our research
% \end{itemize}

>>>>

\usepackage[english]{babel}
\usepackage{url}
\usepackage{makecell}

@@

@@

Let $s$ be the generated summary. If $|s|$ is the number of words in summary $s$, then $m=|s|-n+1$ is the number of $n$-grams in this summary. Let $s_1, s_2, \dots, s_m$ be all $n$-grams of summary $s$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important $n$-grams in the document. As we will show in section \ref{sec:importance}, there are many ways of measuring the importance of $n$-grams in a document. The definition of $n$-gram importance is closely related to the two base assumptions that were mentioned at the beginning of section \ref{sec:evaluation}.

@@

\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]

@@

\subsection{TextRank}
In this research we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score.

\begin{table}[H]
\caption{Example of an abstract generated by our model}

\begin{center}
\begin{tabular}{|p{0.25\linewidth}|p{0.67\linewidth}|}
\hline
\textbf{Title} & Churn Prediction in Mobile Social Games: Towards a Complete Assessment Using Survival Ensembles \\
\hline
\textbf{Real abstract} & ...for each player, we predict the probability of churning as function of time, which permits to distinguish various levels of loyalty profiles ... Our results show that churn prediction by survival ensembles significantly improves the accuracy and robustness of traditional analyses, like Cox regression... \\
\hline
\textbf{\makecell[l]{Generated \\ abstract}} & Conditional inference survival ensembles are constructed based on unbiased trees avoiding this problem the resulting prediction of this model contains for each player a survival function indicating the probability of churn as a function of time since the registration in the game. \\
\hline
\end{tabular}
\end{center}
\end{table}

\subsection{Seq2Seq}
We have used seq2seq model with attention for a task of text summarization. Seq2seq have proven to provide state-of-art result in tasks of sequence generation.
As input model takes paper abstract converted to the vectorized representation using word embeddings.  The input sequence is limited by 600 words. All abstracts that are bigger than limit are omitted. All smaller abstracts are padded with $\langle\text{SOS}\rangle$ word that represents the end of a sequence.
Model outputs sequence derived from the probability distribution. Each output word samples from this distribution having input sequence and previously generated samples. Output sequence is limited by 30 words. First $\langle\text{SOS}\rangle$ word represent the end of a generated summary.

@@

\begin{table}[H]
\caption{Evaluating different models with ROUGE}

\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} \\
\hline
TextRank & 18.04 & 4.10 & 10.89 \\
LSTM & 0 & 0 & 0 \\
SeqGAN & 0 & 0 & 0 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@
